Comparing, High/Low performers

### 2023-08-14 Misc/e1_brms_test.qmd
Indv tables function, and some reorganization

e1_testDistRF2_0 |> spread_draws(b_conditConstant,b_conditVaried,b_vb[vb,])

e1_testDistRF2_0 |> spread_draws(r_id[id,term]) |> head(10)

e1_testDistRF2_0 |> spread_draws(b_conditConstant,b_conditVaried) |> compare_levels(condit)

>>>>

model_parameters(e1_testDistRF2_0,effects="random",keep="^r_id\\[3,.*\\]")
plot_subject_fits(e1_testDistRF2_0,3)

indvFit <- GetIndvFits(e1_testDistRF2_0)

indvFit |> ggplot(aes(x=condit,y=Median,fill=condit))+stat_halfeye()+facet_wrap(~vb)

### 2023-08-14 Misc/gam_discrim.qmd
Indv tables function, and some reorganization

```{r}
pacman::p_load(tidyverse,lme4,emmeans,here,knitr,kableExtra,gt,mgcv,data.table)
e1 <- readRDS(here("data/e1_07_27_23.rds"))
source(here("Functions/Display_Functions.R"))

>>>>

```{r}
pacman::p_load(tidyverse,lme4,emmeans,here,knitr,kableExtra,gt,mgcv,data.table)
e1 <- readRDS(here("data/e1_08-04-23.rds"))
source(here("Functions/Display_Functions.R"))

### 2023-08-14 Misc/quartile_splits.qmd
Indv tables function, and some reorganization

```{r setup}
pacman::p_load(tidyverse,lme4,emmeans,here,knitr,kableExtra,gt,gghalves)
e1 <- readRDS(here("data/e1_07-27-23.rds"))
source(here("Functions/Display_Functions.R"))

>>>>

```{r setup}
pacman::p_load(tidyverse,lme4,emmeans,here,knitr,kableExtra,gt,gghalves)
e1 <- readRDS(here("data/e1_08-04-23.rds"))
source(here("Functions/Display_Functions.R"))
